The contribution of blowing snow to cloud properties and the atmospheric radiative budget over Antarctica

### 2020-11-25 manuscript/manuscript.tex
WIP heatmaps# Please enter the commit message for your changes. Lines starting

\textbf{Antarctica and its surroundings are one of the main areas for biases in climate models, mostly due to uncertainties in the representation of clouds. Over the Antarctic Ice Sheet, temperature inversions and strong temperature gradients between the cold interior and the edges lead to strong katabatic downslope winds, transporting snow and moisture from the interior towards the peripheral regions at the southern edge of the Southern Ocean’s storm track. These blowing snow layers are usually 100-200 m thick, but can reach a thickness of more than 500 m and can be advected offshore from Antarctica over open ocean waters (Scarchili et al., 2010; Palm et al., 2017). However, the impacts of moisture and wind-induced snow mass transport (i.e. ice nucleating particles) on cloud structure and development over Antarctica has not been thoroughly investigated and most state-of-the-art climate models do not account for its presence. Here, we use a regional climate model with a newly developed fully active blowing snow scheme and satellite data, to show that accounting for drifting snow notably alters the spatial distribution, vertical structure and radiative contribution of clouds over Antarctica and its periphery. Additionally, our results indicate that the advection of blowing snow and air with a higher humidity content over the Southern Ocean also impacts clouds and their microphysics in areas outside of Antarctica. While our study area is limited to 60S, our results highlight the need to study the impact of missing blowing snow processes on the future evolution of clouds not just over Antarctica, but potentially also over the Southern Ocean, an area with significant uncertainties in future climate projections.}

@@

Accounting for blowing snow also alters the cloud radiative effect (Fig.\ref{fig:Test} C). While we see the strongest effects again in the boundary layer, especially over the steeper margins the CRE is altered to elevations of up to 5000 m. This vertical influence on the CRE might be due to the fact that airborne blowing snow particles can be mixed to layers above the boundary layer in zones with stronger adiabatic mixing and turbulence, i.e. over the steeper slopes where the katabatic winds are the strongest. Subsequently, these additional ice crystals can influence the macrophysical cloud properties (IWP, LWP and COD), and therefore the CRE. Additionally, because of changes in the vertical temperature distribution and humidity due to blowing snow sublimation, also the effectiveness and temperature of the layers that emit the longwave radiation can be altered between the two simulations.

@@

\begin{figure}[H]
	\includegraphics[scale=0.7,center]{microphysics.png}
	\caption{\textbf{Difference in cloud properties between MAR with and without blowing snow.} A) Difference in cloud cover (\%) between the two MAR simulations. Red colors indicate a greater cloud cover percentage in MAR with active blowing snow parameterisation. B) Same as A) but for the difference in cloud optical depth (COD, unitless) between the two MAR simulations. C) Same as A) but for the difference in liquid water path(LWP, g/kg). D) Same as A) but for the difference in ice water path (IWP, g/kg).}
	\label{fig:micro}
\end{figure}

>>>>

\textbf{Over Antarctica and the Southern Ocean climate models often struggle to correctly model clouds. Over the Antarctic Ice Sheet, temperature inversions and strong temperature gradients between the cold interior and the edges lead to strong katabatic downslope winds, transporting snow and moisture from the interior towards the peripheral regions at the southern edge of the Southern Ocean’s storm track. These blowing snow layers are usually 100-200 m thick, but can reach a thickness of more than 500 m and can be advected offshore from Antarctica over open ocean waters (Scarchili et al., 2010; Palm et al., 2017). However, the impacts of moisture and wind-induced snow mass transport (i.e. ice nucleating particles) on cloud structure and development over Antarctica has not been thoroughly investigated and most state-of-the-art climate models do not account for its presence. Here, we use a regional climate model with a newly developed fully active blowing snow scheme and satellite data, to show that accounting for drifting snow notably alters the spatial distribution, vertical structure and radiative contribution of clouds over Antarctica and its periphery. Additionally, our results indicate that the advection of blowing snow and air with a higher humidity content over the Southern Ocean also impacts clouds and their microphysics in areas outside of Antarctica. While our study area is limited to 60S, our results highlight the need to study the impact of missing blowing snow processes on the future evolution of clouds not just over Antarctica, but potentially also over the Southern Ocean, an area with significant uncertainties in future climate projections.}

@@

Accounting for blowing snow also alters the cloud radiative effect (Fig.\ref{fig:Test} C). While we see the strongest effects again in the boundary layer, especially over the steeper margins the CRE is altered to elevations of up to 5000 m. This vertical influence on the CRE might be due to the fact that airborne blowing snow particles can be mixed to layers above the boundary layer in zones with stronger adiabatic mixing and turbulence, i.e. over the steeper slopes where the katabatic winds are the strongest. Subsequently, these additional ice crystals can influence the macrophysical cloud properties (IWP, LWP and COD), and therefore the CRE. Additionally, because of changes in the vertical temperature distribution and humidity due to blowing snow sublimation, also the effectiveness and temperature of the layers that emit the longwave radiation can be altered between the two simulations. 
\begin{figure}[H]
	\includegraphics[scale=0.7,center]{microphysics.png}
	\caption{\textbf{Difference in cloud properties between MAR with and without blowing snow.} A) Difference in cloud cover (\%) between the two MAR simulations. Red colors indicate a greater cloud cover percentage in MAR with active blowing snow parameterisation. B) Same as A) but for the difference in cloud optical depth (COD, unitless) between the two MAR simulations. C) Same as A) but for the difference in liquid water path(LWP, g/kg). D) Same as A) but for the difference in ice water path (IWP, g/kg).}
	\label{fig:micro}
\end{figure}

@@

Changes in cloud macrophysical properties due to blowing snow go hand-in-hand with changes in the surface energy budget \cite{Hofer2019}. In the shortwave part of the spectrum, our simulation with blowing snow models less incoming solar radiation over Antarctica (Fig.\ref{fig:SEB}A), mostly due to an increase in cloud cover, and a slight increase in IWP (Fig.\ref{fig:micro}A,D). On average, over the Antarctica Ice Sheet the SWD decrease is \textbf{XX $\pm$ XX Wm\textsuperscript{-2}}. Conversely, over the open ocean we see a notable increase in SWD by up to \textbf{XX}, related to a coincident decrease in cloud cover, LWP, IWP and subsequently also cloud optical depth (Fig. \ref{fig:SEB}A, Fig.\ref{fig:micro}A-D).The second external driver of the surface energy budget, downwelling longwave radiation, our simulation with blowing snow shows the opposite effect: LWD increases over all the Antarctic Ice Sheet (\textbf{mean XX Wm2}, while it decreases over the ocean due to competing effects of changes in the cloud macrophysics upon the SW and LW CRE (\textbf{CITE XX}).

When looking at the net radiative effect of blowing snow (Fig. \ref{fig:SEB}C), we see that including blowing snow leads to a net warming of \textbf{+ XX WM2} over the Antarctic Ice Sheet. Here, the warming effect is mostly caused by an increase in LWD, most notably over the steep margins. Over the sloping terrain we see an increase in cloud cover, together with the strongest increase in cloud IWP (enhanced WBF process?), causing an enhanced cloud longwave emissivity (Fig. \ref{fig:micro}D). Conversely, we also see a net cooling effect over open ocean, where we see a decrease in CC, COD, LWP and IWP (Fig.\ref{fig:micro}A-D). However, for future sea level rise projections, the most important result is that blowing snow can induce a warming over Antarctica, where it can potentially enhance melt and mass loss rates over the grounded ice part of Antarctica (Fig.\ref{fig:SEB}C).
